---
title: "Project 3"
author: "Kamlesh Pandey"
date: "11/9/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library  
```{r lib_import, warning=FALSE, message=FALSE}
library(dplyr)
library(readr)
library(ggplot2)

```

# Introdcution  
We are living in a digital world where we are more concerned about our digital footprint and people often look toward the like and share they get on a post that they publish online. We have several social media websites and print media to share our articles. Online print media platform like [Mashable](www.mashable.com) publishes thousand of online media everyday and it is important for them get a more user engagement from the the article they post online. In this dataset we are trying to predict the share based on several predictor columns such as text sentiment polarity, rate of negative words, rate of positive words, and many more.
Why this analysis is important ? From this predictive model, Mashable can predict the number of share they can receive based on the type of article they are publishing online.  


# Data
The dataset summarizes a heterogeneous set of features about articles published by in a period of two years.The dataset has 39644 data points and 61 feature columns. The project is aimed to subset the original dataset based on type of data channel (one of the six type) and then to predict the number of shares variable. For this project we are using ..... for training and building a predictive modeling and eventually same analysis will be used for remaining five data channel. User will have flexibility to choose the type of analysis they want based on their personal choice.  
```{r dataset, warning=FALSE, message=FALSE}
newpopData <- readr::read_csv('OnlineNewsPopularity.csv',
                              locale = locale(encoding = 'latin1'))
head(newpopData,5)
```  
# Exploratory Data Analysis  
Before starting EDA, target variable need to be normalize as it has high standard deviation (11600).
```{r eda, warning=FALSE, message=FALSE}
data("newpopData", package = "ggplot2")
newpopData$scaledShare <- scale(newpopData$shares, center = T, scale = T)
# scatterplot
gg <- ggplot(newpopData, aes(x= n_tokens_content, y = scaledShare)) +
  geom_point()+
  labs(subtitle = 'Word Count Vs Number of Share',
       y = 'Number of Share (Scaled)',
       x = 'Number of Words in article', 
       title = 'Scatterplot',
       caption = 'Source: News Popularity Dataset')
plot(gg)
```
